\section{The heads blend}
\paragraph \\
At the core of the heads build system is a file called
\textbf{heads.blend}. A \emph{blend} is a concept I developed for
libdevuansdk\footnotemark. Since you probably have no idea what
libdevuansdk even is, I'll start by getting a bit into that one first.

\subsection{libdevuansdk}
\paragraph \\
\emph{libdevuansdk} is a shell script library that emerged when I began
maintaining the Devuan SDK\footnotemark. The Devuan SDK\footnotemark
is a small framework written in zsh, and currently consists of libdevuansdk
as such, and wrappers that are supposed to be written around it. Currently:
\emph{arm-sdk}, \emph{live-sdk}, and \emph{vm-sdk}. heads' build system
utilizes the live-sdk.

\paragraph \\
libdevuansdk gathers common knowledge that is utilized by the beforementioned
sdks, and as the name says - is a common library of sorts. All functions that
are not declared in the heads blend, are either a part of live-sdk or
libdevuansdk. The concept is such that the blend can override functions of what
is above it (live-sdk, and then libdevuansdk). live-sdk does the same. This
makes it easy to do situation-specific overrides while not breaking the API.

\subsection{Configuration}
\paragraph \\
The first thing the blend does is sourcing a config file. The config file is
where all the software versions, their locations, list of packages to install
and remove are kept.

\paragraph \\
\textbf{extra\_packages} is an array of Devuan package names that we append to
because it is already a part of libdevuansdk and live-sdk. This array holds
all software installed in heads that exists as a package in the Devuan
repositories.

\paragraph \\
\textbf{purge\_packages} is an array of packages that should be purged from the
system when it's the time to do it (in a certain step of libdevuansdk).

\paragraph \\
\textbf{finalize\_purge\_packages} is an array of packages that should be purged
from the system at the final blend step. It is an array specific to the blend.

\footnotetext[4]{\url{https://git.devuan.org/sdk/libdevuansdk}}
\footnotetext[5]{\url{https://git.devuan.org/sdk/}}
\footnotetext[6]{Simple Distro Kit}
